Are We Reusing Outdated and License-Violating Code Snippets from Stack Overflow?

### 2017-02-08 cloneoverflow-latex/cloneoverflow.tex

A motivating example of outdated online code clones can be found in the a Stack Overflow post regarding how to implement \textit{RawComparator} in \texttt{hadoop}\footnote{http://stackoverflow.com/questions/22262310}. In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question. The snippet shows how \texttt{hadoop} implements \textit{compare} method in its \textit{WritableComparator} class. The code snippet on the right hand side shows another version of the same \textit{compare} method in \textit{WritableComparator} class but it is extracted from the latest version of \texttt{hadoop}. We can obviously see that they are highly similar except one line, \verb|buffer.reset(null,0,0);|, is added in the latest version after \verb|key2.readFields(buffer);|. The added line is intended for cleaning up the reference in \verb|buffer| variable. While this change has already been introduced into \textit{compare} method in the latest version of \texttt{hadoop}, the code example in Stack Overflow post is still unchanged. This example shows that there can be inconsistencies between online code clones and its original. The code snippet on Stack Overflow can be outdated.  %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases. 
%This is an emerging and challenging problem. Since studies in this area are still limited, we aim to gain more insight of the problem in this study. %We are interested to gain more insights of online code clone in this study.

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textit{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between \texttt{<code></code>} tags. A Stack Overflow thread contains a post of question and several posts of answers. Every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets which were smaller than six lines were usually spurious clones \cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accept answers because they actually solved the problems in the questions and had a check mark sign on them to notify other users. Moreover, they were always displayed just below the questions which made them attractive to be reused than other answers. Each snippet was extracted from the dump using regular expressions and saved to a file using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added \texttt{.java} extension to the file's names so that clone detectors could recognise them. We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations \FIXME{boxplots here?}}
	\label{tab:raw_stats}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.84 & 5.33 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
	}
\end{table}

@@

\begin{table}
	\centering
	\caption{Distribution of the agreed clone pairs}
	\label{t_agreed_good_clone_pairs}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r}
		\hline
		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Total & Unique \\
		\hline
		\textit{good} & 18 & 26 & 10 & 2,267 & 2,321 & 2,308 \\
		\textit{ok} & 11,467 & 993 & 79 & 20,021 & 32,560 & 31,729  \\
		\hline
	\end{tabular} %
}
\end{table}

@@

In our clone classification process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the \texttt{equals()} pairs came from \textit{ok} and $S_D$ pairs). Finally, there are 3,502 pairs remaining which we manually classified them. The classification summary is shown in \Cref{tab:online_clone_classification_results}.

@@

Nevertheless, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as pattern BP. We then added 6 new patterns observed as common cloning patterns from our preliminary study. The seven patterns include QS, SQ, UN, ES, BP, IN, and FC as presented in \Cref{tab:classification_scheme}. QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation/links in Stack Overflow post). Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is the opposite of QS. UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones but without any attribution of copying. They are unique enough not be boiler-plate and inheritance or interface implementation. ES (\textbf{Ex}ternal Sources) is a cloning that has an evidence of copying from an external source(s). Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of \verb|equals()| methods, getters and setters, or IDE-generated code (e.g.~GUI components). Pattern IN (\textbf{In}heritance/Interface) is cloning because of inheritance of the same super class or implementation of the same interface. They usually share similar overriding methods. The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents false clone pairs. They can be either accidentally similar clones (e.g.~similar \texttt{try-catch} statements), similar clones after code normalisation, or just false positives of the tools. Using the classification patterns, we can also calculate the number of true and false positives. We are looking for unique and meaningful clones in this study. Thus, we consider clone pairs classified into pattern QS, SQ, UD, and EX as true positive, and BP, IN, and AC as false positive.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{classification_process}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

\textbf{UD: Unknown Direction.} We found 382 online clone pairs with no evidence of cloning between Qualitas and Stack Overflow but with high code similarity. They include 11, 42, 294, and 35 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively. The most cloned projects in this pattern was \texttt{netbeans} which had 95 clone pairs. Most of the clones were large chunk of code involving GUI components which might also be auto-generated. However, we also did not have any evidence. The second most cloned project was \texttt{jung2} (62 pairs) that was a network and graph framework. There were several Stack Overflow snippets that were identical to code in \texttt{jung2}. The third project was \texttt{eclipse-SDK} (37 pairs).

\textbf{EX: External Sources.} We found 178 online clone pairs with evidences of cloning from external sources to Stack Overflow. They include 4, 23, 145, and 6 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
%\begin{table}[]
%	\centering
%	\caption{31 external clones found in Stack Overflow posts}
%	\label{tab:ext_clones}
%	\begin{tabular}{l|r|r}
%		\hline
%		Type        & FOSS & Web \\ \hline
%		StackOverflow only     & 1    & 1   \\
%		StackOverflow + Qualitas & 15   & 14  \\ \hline
%	\end{tabular}
%\end{table}
This findings complement a study of inter clones between software projects \cite{Svajlenko2014}. We show that, besides software projects, clones can also be copied over different websites on the Internet. There are 15 clone pairs that are originated from programming websites. For example, we found a clone of code snippet to convert numbers into words which is copied from \texttt{www.rgagnon.com/javadetails/java-0426.html}. Both Stack Overflow and \texttt{compiere} project source code contain attribution to the original source. Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from \texttt{mrl.nyu.edu/\textasciitilde perlin/noise/}. This code is used in both Stack Overflow and \texttt{aoi} project with attribution. %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license. 
There were 12 pairs cloned from \texttt{zxing}, \texttt{jasper}, \texttt{java.util}, \texttt{javax.servlet}, and \texttt{org.bouncycastle.crypto} project.

\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs found in this study. Although we surly removed some of the boiler-plate code with filters before the analysis, we still observed 28,642 BP clone pairs which accounted for 89.7\% of all clone pairs we classified. The majority of them were \texttt{equals()} methods.

\textbf{IN: Inheritance/interface.} There were 109 clone pairs found to be similar because they implemented the same interface or inheriting from the same class. An example was two implementations of \texttt{MouseListener} that share similar \texttt{@Override} methods of \texttt{mousePressed}, and \texttt{mouseReleased}.

\textbf{AC: Accidental Clones.} 31,946 were clone pairs that were accidentally similar due to several reasons. Mainly, they were caused by the effects of code normalisation applied to the source code before detection. However, the original source code were still different enough when we manually classified them. Other causes include \texttt{finally} or \texttt{try-catch} clauses that were accidentally the same due to their very small sizes, or clearly non-cloned code which may somehow miss the tools' detections.

@@

\Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow. We discovered 59 outdated online clone pairs out of 110 pairs. \texttt{spring} and \texttt{hibernate} have the maximum number of 20 outdated pairs, followed by 15 from \texttt{eclipse}, and 12 from \texttt{hadoop}. An example of outdated code in \texttt{hadoop}'s \texttt{WritableComparator.java} has already been shown in \Cref{fig:before-after}. We also found a few outdated code which contained heavy modifications. For example, the code snippet in Stack Overflow post 23520731, a copy of \texttt{SchemaUpdate.java} in \texttt{hibernate}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}). We also found 3 ``dead'' snippets. These snippets did not have their originals in the latest version of the projects anymore. For example, the snippet in Stack Overflow post 3758110, a copy of \texttt{DefaultAnnotationHandlerMapping.java} in \texttt{spring}, was deleted in commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted. %The latest version of Spring does not contain the file anymore.

@@

	\begin{tabular}{r|l|c|l|c|p{5.8cm}|r|r|c|c|c}

@@

We analysed licensing conflicts of online clones in QS, UD, and EX set. The summary of licensing information is listed in \Cref{tab:license_abc}. The licenses were extracted by Ninka, an automatic license identification tool \cite{German2010}. Since Ninka worked at file level, we report the findings based on Stack Overflow snippets and Qualitas source files instead of clone pairs (duplicates were ignored). For the ones that could not be automatically identified by Ninka and had been reported as \texttt{SeeFile} and \texttt{Unknown}, we looked at them manually.  The table shows license of Stack Overflow snippets and Qualitas source code. The results were reported in groups of QS, UD, and EX. Overall we can see that most of the Stack Overflow snippets do not contain licensing terms while their clone counterparts in Qualitas project do.

>>>>

A motivating example of outdated online code clones can be found in the a Stack Overflow post regarding how to implement {\small{\texttt{RawComparator}}} in \texttt{hadoop}\footnote{http://stackoverflow.com/questions/22262310}. In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question. The snippet shows how {\small{\texttt{hadoop}}} implements {\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}} class. The code snippet on the right hand side shows another version of the same {\small{\texttt{compare}}} method in {\small{\texttt{WritableComparator}}} class but it is extracted from the latest version of {\small{\texttt{hadoop}}}. We can obviously see that they are highly similar except one line, {\small{\verb|buffer.reset(null,0,0);|}}, is added in the latest version after {\small{\verb|key2.readFields(buffer);|}}. The added line is intended for cleaning up the reference in {\small{\verb|buffer|}} variable. While this change has already been introduced into {\small{\texttt{compare}}} method in the latest version of {\small{\texttt{hadoop}}}, the code example in Stack Overflow post is still unchanged. This example shows that there can be inconsistencies between online code clones and its original. The code snippet on Stack Overflow can be outdated.  %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases. 
%This is an emerging and challenging problem. Since studies in this area are still limited, we aim to gain more insight of the problem in this study. %We are interested to gain more insights of online code clone in this study.

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{{\small\texttt{https://archive.org/details/stackexchange}}} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of question and several posts of answers. Every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets which were smaller than six lines were usually spurious clones \cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accept answers because they actually solved the problems in the questions and had a check mark sign on them to notify other users. Moreover, they were always displayed just below the questions which made them attractive to be reused than other answers. Each snippet was extracted from the dump using regular expressions and saved to a file using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: {\small\texttt{https://github.com/AlDanial/cloc}}}.

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations \FIXME{boxplots here?}}
	\label{tab:raw_stats}
	\small
%	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.84 & 5.33 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
%	}
\end{table}

@@

\begin{table}
	\centering
	\caption{Distribution of the agreed clone pairs}
	\label{t_agreed_good_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r}
		\hline
		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Total & Unique \\
		\hline
		\textit{good} & 18 & 26 & 10 & 2,267 & 2,321 & 2,308 \\
		\textit{ok} & 11,467 & 993 & 79 & 20,021 & 32,560 & 31,729  \\
		\hline
	\end{tabular} %
%}
\end{table}

@@

In our clone classification process, we used a script to automatically classify {\small\texttt{equals()}} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the {\small\texttt{equals()}} pairs came from \textit{ok} and $S_D$ pairs). Finally, there are 3,502 pairs remaining which we manually classified them. The classification summary is shown in \Cref{tab:online_clone_classification_results}.

@@

Nevertheless, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as pattern BP. We then added 6 new patterns observed as common cloning patterns from our preliminary study. The seven patterns include QS, SQ, UN, ES, BP, IN, and FC as presented in \Cref{tab:classification_scheme}. QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation/links in Stack Overflow post). Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is the opposite of QS. UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones but without any attribution of copying. They are unique enough not be boiler-plate and inheritance or interface implementation. ES (\textbf{Ex}ternal Sources) is a cloning that has an evidence of copying from an external source(s). Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters and setters, or IDE-generated code (e.g.~GUI components). Pattern IN (\textbf{In}heritance/Interface) is cloning because of inheritance of the same super class or implementation of the same interface. They usually share similar overriding methods. The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents false clone pairs. They can be either accidentally similar clones (e.g.~similar {\small\texttt{try-catch}} statements), similar clones after code normalisation, or just false positives of the tools. Using the classification patterns, we can also calculate the number of true and false positives. We are looking for unique and meaningful clones in this study. Thus, we consider clone pairs classified into pattern QS, SQ, UD, and EX as true positive, and BP, IN, and AC as false positive.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.6\linewidth]{classification_process}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

\textbf{UD: Unknown Direction.} We found 382 online clone pairs with no evidence of cloning between Qualitas and Stack Overflow but with high code similarity. They include 11, 42, 294, and 35 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively. The most cloned projects in this pattern was {\small{\texttt{netbeans}}} which had 95 clone pairs. Most of the clones were large chunk of code involving GUI components which might also be auto-generated. However, we also did not have any evidence. The second most cloned project was {\small{\texttt{jung2}}} (62 pairs) that was a network and graph framework. There were several Stack Overflow snippets that were identical to code in {\small{\texttt{jung2}}}. The third project was {\small{\texttt{eclipse-SDK}}} (37 pairs).

\textbf{EX: External Sources.} We found 178 online clone pairs with evidences of cloning from external sources to Stack Overflow. They include 4, 23, 145, and 6 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
%\begin{table}[]
%	\centering
%	\caption{31 external clones found in Stack Overflow posts}
%	\label{tab:ext_clones}
%	\begin{tabular}{l|r|r}
%		\hline
%		Type        & FOSS & Web \\ \hline
%		StackOverflow only     & 1    & 1   \\
%		StackOverflow + Qualitas & 15   & 14  \\ \hline
%	\end{tabular}
%\end{table}
This findings complement a study of inter clones between software projects \cite{Svajlenko2014}. We show that, besides software projects, clones can also be copied over different websites on the Internet. There are 15 clone pairs that are originated from programming websites. For example, we found a clone of code snippet to convert numbers into words which is copied from {\small{\texttt{www.rgagnon.com/javadetails/java-0426.html}}}. Both Stack Overflow and \texttt{compiere} project source code contain attribution to the original source. Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from {\small{\texttt{mrl.nyu.edu/\textasciitilde perlin/noise/}}}. This code is used in both Stack Overflow and \texttt{aoi} project with attribution. %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license. 
There were 12 pairs cloned from {\small{\texttt{zxing}}}, {\small{\texttt{jasper}}}, {\small{\texttt{java.util}}}, {\small{\texttt{javax.servlet}}}, and {\small{\texttt{org.bouncycastle.crypto}}} project.

\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs found in this study. Although we surly removed some of the boiler-plate code with filters before the analysis, we still observed 28,642 BP clone pairs which accounted for 89.7\% of all clone pairs we classified. The majority of them were {\small{\texttt{equals()}}} methods.

\textbf{IN: Inheritance/interface.} There were 109 clone pairs found to be similar because they implemented the same interface or inheriting from the same class. An example was two implementations of {\small{\texttt{MouseListener}}} that share similar {\small{\texttt{@Override}}} methods of {\small{\texttt{mousePressed}}}, and {\small{\texttt{mouseReleased}}}.

\textbf{AC: Accidental Clones.} 31,946 were clone pairs that were accidentally similar due to several reasons. Mainly, they were caused by the effects of code normalisation applied to the source code before detection. However, the original source code were still different enough when we manually classified them. Other causes include {\small{\texttt{finally}}} or {\small{\texttt{try-catch}}} clauses that were accidentally the same due to their very small sizes, or clearly non-cloned code which may somehow miss the tools' detections.

@@

\Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow. We discovered 59 outdated online clone pairs out of 110 pairs. {\small{\texttt{spring}}} and {\small{\texttt{hibernate}}} have the maximum number of 20 outdated pairs, followed by 15 from {\small{\texttt{eclipse}}}, and 12 from {\small{\texttt{hadoop}}}. An example of outdated code in {\small{texttt{hadoop}}}'s {\small{\texttt{WritableComparator.java}}} has already been shown in \Cref{fig:before-after}. We also found a few outdated code which contained heavy modifications. For example, the code snippet in Stack Overflow post 23520731, a copy of {\small{\texttt{SchemaUpdate.java}}} in {\small{\texttt{hibernate}}}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}). We also found 3 ``dead'' snippets. These snippets did not have their originals in the latest version of the projects anymore. For example, the snippet in Stack Overflow post 3758110, a copy of {\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in {\small{\texttt{spring}}}, was deleted in commit {\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted. %The latest version of Spring does not contain the file anymore.

@@

	\begin{tabular}{r|l|c|l|c|p{5cm}|r|r|c|c|c}

@@

We analysed licensing conflicts of online clones in QS, UD, and EX set. The summary of licensing information is listed in \Cref{tab:license_abc}. The licenses were extracted by \textbf{Ninka}, an automatic license identification tool \cite{German2010}. Since Ninka worked at file level, we report the findings based on Stack Overflow snippets and Qualitas source files instead of clone pairs (duplicates were ignored). For the ones that could not be automatically identified by Ninka and had been reported as {\small\texttt{SeeFile}} and {\small\texttt{Unknown}}, we looked at them manually.  The table shows license of Stack Overflow snippets and Qualitas source code. The results were reported in groups of QS, UD, and EX. Overall we can see that most of the Stack Overflow snippets do not contain licensing terms while their clone counterparts in Qualitas project do.
